\begin{acknowledgment}
	The authors would like to thank first and foremost the Almighty God for giving them strength and courage to finish this research study. And their parents for the unending love and support.
	
	The researchers extend their heartfelt gratitude and appreciation to their thesis advisers, Mr. Aarhus M. Dela Cruz and Dr. Aaron Paul Dela Rosa for their unwavering support, patience, and guidance that made the development of this thesis possible.
	
	The researchers also send their sincere appreciation for the defense panel who gave their valuable comments and critique to improve the system. Along with the evaluators from Bulacan State University's ICTO and CICT, and the professionals from outside the university for their insightful suggestions.
	
	The researchers also extend their gratitude for the Provincial History, Arts, Culture, and Tourism Office (PHACTO) for their assistance in providing the necessary data for the development. And special thanks to the local government units who accepted our requests in service of the public.
	
	% mandatory acknowledgement to the creator of the bulsu thesis template files
	% do no delete
	Special thanks to the creator of bulsuthsis.cls, and its accompanying files thesis.tex and thesis-structure.tex, Mr. Harris R. Dela Cruz. With these, the authors were able to typeset conveniently and efficiently an elegant and beautiful thesis manuscript.
	% do no delete
	% mandatory acknowledgement to the creator of the bulsu thesis template files
	
	Furthermore, the researchers would like to thank their respective friends and significant others in their unwavering support and understanding, serving as an invaluable inspiration throughout the journey.
	
	This research would not have been possible without all of you, thank you all.
	
	\begin{flushright}
		Bryan C. Declaro 
		
		Franniel Luigi C. Hilario 
		
		Brian Gabriel G. Magbanua 
		
		Richard M. Manansala 
	\end{flushright}
	
\end{acknowledgment}