\singlespacing
\footnotesize
\begin{longtable}{p{0.67\linewidth} c c c c c}
\caption{System Acceptance Evaluation Frequency Scores} \label{tab:evaluation_scores} \\
\toprule
\multirow{2}{*}{\textbf{Items}} & \multicolumn{5}{c}{\textbf{Frequency}} \\
\cmidrule(l){2-6}
& \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} \\
\midrule
\endfirsthead

\multicolumn{6}{c}%
{{\tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\multirow{2}{*}{\textbf{Items}} & \multicolumn{5}{c}{\textbf{Frequency}} \\
\cmidrule(l){2-6}
& \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} \\
\midrule
\endhead

\midrule
\multicolumn{6}{r}{{Continued on next page}} \\
\endfoot

\bottomrule
\endlastfoot

\multicolumn{6}{l}{\textbf{Perceived Usefulness (PU)}} \\
\midrule
\textbf{Improvement in Performance.} Using the system improves my performance in planning trips. & 0 & 0 & 3 & 52 & 95 \\
\textbf{Task Efficiency.} The system helps me accomplish travel planning tasks more quickly. & 0 & 0 & 3 & 30 & 117 \\
\textbf{Productivity.} The system increases my productivity in organizing itineraries. & 0 & 0 & 1 & 54 & 95 \\
\textbf{Effectiveness.} The system enhances my effectiveness in planning travel activities. & 0 & 0 & 4 & 38 & 108 \\
\textbf{Usefulness.} Overall, I find the system useful for travel planning. & 0 & 0 & 1 & 23 & 126 \\
\midrule

\multicolumn{6}{l}{\textbf{Perceived Ease of Use (PEOU)}} \\
\midrule
\textbf{Ease of Learning.} Learning to operate the system is easy for me. & 0 & 0 & 5 & 43 & 102 \\
\textbf{Ease of Use.} The system is easy to use. & 0 & 0 & 2 & 39 & 109 \\
\textbf{Clarity of Interaction.} My interaction with the system is clear and understandable. & 0 & 0 & 2 & 37 & 111 \\
\textbf{Ease of Becoming Skillful.} I find it easy to become skillful at using the system. & 0 & 0 & 10 & 30 & 110 \\
\textbf{Ease of Operation.} I find the system easy to operate. & 0 & 0 & 3 & 27 & 120 \\
\midrule

\multicolumn{6}{l}{\textbf{Attitude Toward Using (ATU)}} \\
\midrule
\textbf{Positive Feelings.} I have a positive attitude towards using the system. & 0 & 0 & 3 & 29 & 118 \\
\textbf{Enjoyment.} I enjoy using the system. & 0 & 0 & 4 & 37 & 109 \\
\textbf{Satisfaction.} I am satisfied with using the system. & 0 & 0 & 3 & 40 & 107 \\
\midrule

\multicolumn{6}{l}{\textbf{Behavioral Intention to Use (BI)}} \\
\midrule
\textbf{Intention to Use.} I intend to use the system regularly. & 0 & 2 & 15 & 67 & 66 \\
\textbf{Future Use.} I will continue to use the system in the future. & 0 & 1 & 9 & 45 & 95 \\
\textbf{Recommendation.} I would recommend the system to others. & 0 & 2 & 1 & 23 & 124 \\

\end{longtable}


\begin{longtable}{p{0.67\linewidth} c c c c c}
\caption{System Quality Evaluation Frequency Scores (ISO/IEC 25010)} \label{tab:iso_evaluation} \\
\toprule
\multirow{2}{*}{\textbf{Items}} & \multicolumn{5}{c}{\textbf{Frequency}} \\
\cmidrule(l){2-6}
& \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} \\
\midrule
\endfirsthead

\multicolumn{6}{c}%
{{\tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\multirow{2}{*}{\textbf{Items}} & \multicolumn{5}{c}{\textbf{Frequency}} \\
\cmidrule(l){2-6}
& \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} \\
\midrule
\endhead

\midrule
\multicolumn{6}{r}{{Continued on next page}} \\
\endfoot

\bottomrule
\endlastfoot

\multicolumn{6}{l}{\textbf{A. FUNCTIONAL SUITABILITY}} \\
\midrule
\textbf{Functional Completeness.} The system provides a set of functions that covers all the specified tasks and intended users' objectives. & 0 & 0 & 0 & 4 & 18 \\
\textbf{Functional Correctness.} The system provides accurate results when used by intended users. & 0 & 0 & 0 & 3 & 19 \\
\textbf{Functional Appropriateness.} The system provides functions that facilitate the accomplishment of specified tasks and objectives. & 0 & 0 & 0 & 2 & 20 \\
\midrule

\multicolumn{6}{l}{\textbf{B. PERFORMANCE EFFICIENCY}} \\
\midrule
\textbf{Time Behavior.} The system performs its specified function under specified conditions so that the response time and throughput rates meet the requirements. & 0 & 0 & 0 & 5 & 17 \\
\textbf{Resource Utilization.} The system uses no more than the specified amount of resources to perform its function under specified conditions. & 0 & 0 & 0 & 6 & 16 \\
\textbf{Capacity.} The system meets requirements for the maximum limits of a product parameter. & 0 & 0 & 0 & 4 & 18 \\
\midrule

\multicolumn{6}{l}{\textbf{C. COMPATIBILITY}} \\
\midrule
\textbf{Co-existence.} The system performs its required functions efficiently while sharing a common environment and resources with other products, without detrimental impact on any other product. & 0 & 0 & 0 & 6 & 16 \\
\textbf{Interoperability.} The system can exchange information with other products and mutually use the information that has been exchanged. & 0 & 0 & 2 & 5 & 15 \\
\midrule

\multicolumn{6}{l}{\textbf{D. INTERACTION CAPABILITY}} \\
\midrule
\textbf{Appropriateness Recognizability.} The system can be recognized by users as appropriate for their needs. & 0 & 0 & 0 & 3 & 19 \\
\textbf{Learnability.} The system can have specified users learn to use specified product functions within a specified amount of time. & 0 & 0 & 0 & 4 & 18 \\
\textbf{Operability.} The system has functions and attributes that make it easy to operate and control. & 0 & 0 & 0 & 4 & 18 \\
\textbf{User Error Protection.} The system can prevent operation errors. & 0 & 0 & 1 & 6 & 15 \\
\textbf{User Engagement.} The system presents functions and information in an inviting and motivating manner encouraging continued interaction. & 0 & 0 & 0 & 6 & 16 \\
\textbf{Inclusivity.} The system can be utilized by people of various backgrounds. & 0 & 0 & 0 & 5 & 17 \\
\textbf{User Assistance.} The system can be used by people with the widest range of characteristics and capabilities to achieve specified goals in a specified context of use. & 0 & 0 & 1 & 5 & 16 \\
\textbf{Self-Descriptiveness.} The system can present appropriate information, where needed by the user, to make its capabilities and use immediately obvious to the user without excessive interactions with a product or other resources. & 0 & 0 & 0 & 5 & 17 \\
\midrule

\multicolumn{6}{l}{\textbf{E. RELIABILITY}} \\
\midrule
\textbf{Faultlessness.} The system performs specified functions without fault under normal operation. & 0 & 0 & 1 & 1 & 20 \\
\textbf{Availability.} The system is operational and accessible when required for use. & 0 & 0 & 1 & 2 & 19 \\
\textbf{Fault Tolerance.} The system operates as intended despite the presence of hardware or software faults. & 0 & 0 & 1 & 4 & 17 \\
\textbf{Recoverability.} The system can recover the data directly affected and re-establish the desired state of the system. & 0 & 0 & 0 & 3 & 19 \\
\midrule

\multicolumn{6}{l}{\textbf{F. SECURITY}} \\
\midrule
\textbf{Confidentiality.} The system ensures that data are accessible only to those authorized to have access. & 0 & 0 & 1 & 3 & 18 \\
\textbf{Integrity.} The system ensures that its state and data are protected from unauthorized modification or deletion either by malicious action or computer error. & 0 & 0 & 0 & 4 & 18 \\
\textbf{Non-repudiation.} The system can be proven to have taken place so that the events or actions cannot be repudiated later. & 0 & 0 & 0 & 5 & 17 \\
\textbf{Accountability.} The system enables the actions of an entity to be traced uniquely to the entity. & 0 & 0 & 0 & 1 & 21 \\
\textbf{Authenticity.} The system can prove that the identity of a subject or resource is the one claimed. & 0 & 0 & 0 & 3 & 19 \\
\textbf{Resistance.} The system sustains operations while under attack from a malicious actor. & 0 & 0 & 1 & 3 & 18 \\
\midrule

\multicolumn{6}{l}{\textbf{G. MAINTAINABILITY}} \\
\midrule
\textbf{Modularity.} The system can limit changes to one component from affecting other components. & 0 & 0 & 0 & 8 & 14 \\
\textbf{Reusability.} The system can be used as assets in more than one system, or in building other assets. & 0 & 0 & 0 & 7 & 15 \\
\textbf{Analysability.} The system can be effectively and efficiently assessed regarding the impact of an intended change to one or more of its parts, to diagnose it for deficiencies or causes of failures, or to identify parts to be modified. & 0 & 0 & 1 & 9 & 12 \\
\textbf{Modifiability.} The system can be effectively and efficiently modified without introducing defects or degrading existing product quality. & 0 & 0 & 0 & 7 & 15 \\
\textbf{Testability.} The system can enable an objective and feasible test to be designed and performed to determine whether a requirement is met. & 0 & 0 & 0 & 2 & 20 \\
\midrule

\multicolumn{6}{l}{\textbf{H. FLEXIBILITY}} \\
\midrule
\textbf{Adaptability.} The system can be effectively and efficiently adapted for or transferred to different hardware, software, or other operational or usage environments. & 0 & 0 & 0 & 5 & 17 \\
\textbf{Scalability.} The system can handle growing or shrinking workloads or adapt its capacity to handle variability. & 0 & 0 & 0 & 4 & 18 \\
\textbf{Installability.} The system can be effectively and efficiently installed successfully and/or uninstalled in a specified environment. & 0 & 0 & 0 & 4 & 18 \\
\textbf{Replaceability.} The system can replace another specified product for the same purpose in the same environment. & 0 & 0 & 0 & 9 & 13 \\
\midrule

\multicolumn{6}{l}{\textbf{I. SAFETY}} \\
\midrule
\textbf{Operational Constraint.} The system can constrain its operation to within safe parameters or states when encountering operational hazards. & 0 & 0 & 0 & 3 & 19 \\
\textbf{Risk Identification.} The system can identify a course of events or operations that can expose life, property, or environment to unacceptable risk. & 0 & 0 & 1 & 4 & 17 \\
\textbf{Fail-Safe.} The system can automatically place itself in a safe operating mode, or revert to a safe condition in the event of a failure. & 0 & 0 & 1 & 6 & 15 \\
\textbf{Hazard Warning.} The system can provide warnings of unacceptable risks to operations or internal controls so that they can react in sufficient time to sustain safe operations. & 0 & 0 & 1 & 4 & 17 \\
\textbf{Safe Integration.} The system can maintain safety during and after integration with one or more components. & 0 & 0 & 1 & 3 & 18 \\

\end{longtable}
